---
title: "Normally Explore ..."
author: "James Kim"
date: "3/15/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Normally Explore ...

### **is ...**

### **an all new Shiny Application designed for learning:**
* #### The Normal Distribution (hence "Normally Explore ...")
* #### Statistical Studies using Normal Distribution including
#### a. Student's (Gosset's) T-test (Statistical Inference)
#### b. K-Means Clustering (Predictive Machine Learning)

### **For example ...**

## T-test Using Normal Distribution

* #### Student's T-test on a pair of simulated normal distributions
* #### Customizable number of points, mean, and stdandard deviation for each of the simulated distributions
```{r T-test,echo=FALSE,message=FALSE}
require(plotly)
require(ggplot2)
distr.df<-data.frame(X=c(rnorm(300,-2,1),rnorm(300,2,1.5)),
                     d=c(rep("g",300),rep("p",300)))

x.axis.val<-(-100:100)/10
g.th.distr<-(300/2.75)*0.4*exp(-((-2-x.axis.val))^2/2)
p.th.distr<-(300/2.75/1.5)*0.4*exp(-((2-x.axis.val)/1.5)^2/2)
th.distr.df<-data.frame(X=c(x.axis.val,x.axis.val),
                        Y=c(g.th.distr,p.th.distr),
                        d=c(rep("g",length(x.axis.val)),rep("p",length(x.axis.val))))
g<-ggplot(distr.df,aes(X,fill=d))+
    geom_histogram(position='identity',binwidth=0.4,color='gray',alpha=0.75)+
    xlim(-10,10)+xlab("OBSERVATION")+ylab("FREQUENCY")+theme(legend.position='none')+
    geom_line(data=th.distr.df,aes(x=X,y=Y,color=d),size=1.25)
ggplotly(g)
```

## K-Means Clustering

* #### K-Means Clustering on four distributions on an xy plane
* #### Customizable number of points, mean, and stdandard deviation for each of the simulated distributions
```{r K-Means Clustering,echo=FALSE,message=FALSE}
require(plotly)
require(ggplot2)
distr.df<-data.frame(X=c(rnorm(100,2,1),rnorm(66,-1,1.5),rnorm(100,0,1.25),rnorm(50,2,1.25)),
                     Y=c(rnorm(100,1,1),rnorm(66,2.5,1),rnorm(100,-2,1.5),rnorm(50,5,1.75)),
                     d=c(rep("1",100),rep("2",66),rep("3",100),rep("4",50)))
kmc<-kmeans(distr.df[,1:2],4,20)$centers
g<-ggplot(distr.df,aes(X,Y,color=d))+geom_point(size=2.5,alpha=0.6)+xlim(-10,10)+ylim(-10,10)+
          theme(legend.position='none')+annotate('text',kmc[,1],kmc[,2],label=c("@","@","@","@"))
ggplotly(g)
```

## Offering Excellent "Normal" Learning!

* #### Available worldwide via online access!
* #### Try it out! https://abbagguya.shinyapps.io/normalexploration

```{r clustering,echo=FALSE,message=FALSE}
require(leaflet)
leaflet()%>%addTiles()
```

